Category_Tables

### 2019-09-16 Analysis/Category_Tables.Rmd
Rename size_slope to Fig2

Disease_String_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Coherence.KEGG) %>% filter(!is.na(String.Coherence.KEGG)) %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(String.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(String.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(String.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_String_Filt_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Filt.Coherence.KEGG) %>% filter(!is.na(String.Filt.Coherence.KEGG))   %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Filt.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(String.Filt.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(String.Filt.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(String.Filt.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_Biogrid_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, Biogrid.Coherence.KEGG) %>% filter(!is.na(Biogrid.Coherence.KEGG)) %>% group_by(Category) %>% summarise(Min_Coherence = min(Biogrid.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(Biogrid.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(Biogrid.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(Biogrid.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

@@

Cat_Within = Disease_Sum %>% group_by(Category) %>% summarise(`Number of SNPs`= sum(`Number.of.SNPs`), `Number of Genes` = sum(Number.of.genes), `Total Diseases` = n(),  `Mean Biogrid Coherence` =mean(Biogrid.Coherence.KEGG, na.rm = TRUE), `Mean String Coherence` = mean(String.Coherence.KEGG, na.rm = TRUE), `Mean String Filtered Coherence` = mean(String.Filt.Coherence.KEGG, na.rm = TRUE)) %>% arrange(Category)

@@

ggsave("../manuscript/Figures/Size_Slope_Plot.png", slope_plot, height=5, width=7, units="in", dpi = 600)
```

>>>>

Disease_String_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Coherence) %>% filter(!is.na(String.Coherence)) %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Coherence, na.rm = TRUE), Max_Coherence = max(String.Coherence, na.rm = TRUE), Mean_Coherence = mean(String.Coherence, na.rm = TRUE), Median_Coherence =median(String.Coherence, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_String_Filt_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Filt.Coherence) %>% filter(!is.na(String.Filt.Coherence))   %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Filt.Coherence, na.rm = TRUE), Max_Coherence = max(String.Filt.Coherence, na.rm = TRUE), Mean_Coherence = mean(String.Filt.Coherence, na.rm = TRUE), Median_Coherence =median(String.Filt.Coherence, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_Biogrid_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, Biogrid.Coherence) %>% filter(!is.na(Biogrid.Coherence)) %>% group_by(Category) %>% summarise(Min_Coherence = min(Biogrid.Coherence, na.rm = TRUE), Max_Coherence = max(Biogrid.Coherence, na.rm = TRUE), Mean_Coherence = mean(Biogrid.Coherence, na.rm = TRUE), Median_Coherence =median(Biogrid.Coherence, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

@@

Cat_Within = Disease_Sum %>% group_by(Category) %>% summarise(`Number of SNPs`= sum(`Number.of.SNPs`), `Number of Genes` = sum(Number.of.genes), `Total Diseases` = n(),  `Mean Biogrid Coherence` =mean(Biogrid.Coherence, na.rm = TRUE), `Mean String Coherence` = mean(String.Coherence, na.rm = TRUE), `Mean String Filtered Coherence` = mean(String.Filt.Coherence, na.rm = TRUE)) %>% arrange(Category)

@@

ggsave("../manuscript/Figures/Fig2_Size_Slope_Plot.png", slope_plot, height=5, width=7, units="in", dpi = 600)
```

```{}
